\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-18 manuscript.Rmd
IRT

| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |

@@

| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |

@@

| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |

@@

| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |

@@

| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |

@@

| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |

@@

| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |

@@

| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "Blue Filter")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "Smart Device")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")

@@

Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

@@

@@

F1_item.info <- plot(F1_fit, type = "infotrace", main = "F1")

F2_item.info.redu <- plot(F2_fit.redu, type = "infotrace", main = "F2")

F3_item.info.redu <- plot(F3_fit.redu, type = "infotrace", main = "F3")

F4_item.info.redu <- plot(F4_fit.redu, type = "infotrace", main = "F4")

F5_item.info <- plot(F5_fit, type = "infotrace", main = "F5")

@@

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_item.info, F2_item.info.redu,F3_item.info.redu,F4_item.info.redu,F5_item.info, 
          labels = "AUTO", label_size = 10)

>>>>

| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |

@@

| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |

@@

| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |

@@

| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |

@@

| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |

@@

| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |

@@

| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |

@@

| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "F1")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "F3")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")

@@

Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = "AUTO", label_size = 10)

Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10)

@@

```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v" )

@@

F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")

F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")

F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")

F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")

F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")

@@

```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
          labels = "AUTO", label_size = 10, align = "v" )
